Developing effective theories for single and bilayer graphene using density matrix downfolding

### 2019-08-19 draft.tex
Lowdin

Common approaches to building many-body theories for real materials involve density functional theory (DFT) \cite{PhysRev.140.A1133}.
One-body terms are obtained by projecting the solutions from the DFT band structure onto a single-particle basis \cite{PhysRevLett.87.047003}.
Two-body terms are developed by assuming a screened Coulomb interaction based on constrained DFT, RPA, or other methods \cite{PhysRevB.62.R16219, PhysRevB.70.195104, PhysRevB.88.075106}.
L\''{o}wdin methods and canonical transformations have also been used to develop effective theories \cite{doi:10.1063/1.4802766, PhysRevA.81.013402, doi:10.1063/1.2196410}.
While useful techniques, it is typically impossible to know whether models built from them accurately describe reality, as usually no clear estimate of model quality is provided.

>>>>

Common approaches to building many-body theories for real materials involve density functional theory (DFT) \cite{PhysRev.140.A1133}.
One-body terms are obtained by projecting the solutions from the DFT band structure onto a single-particle basis \cite{PhysRevLett.87.047003}.
Two-body terms are developed by assuming a screened Coulomb interaction based on constrained DFT, RPA, or other methods \cite{PhysRevB.62.R16219, PhysRevB.70.195104, PhysRevB.88.075106}.
L\"owdin methods and canonical transformations have also been used to develop effective theories \cite{doi:10.1063/1.4802766, PhysRevA.81.013402, doi:10.1063/1.2196410}.
While useful techniques, it is typically impossible to know whether models built from them accurately describe reality, as usually no clear estimate of model quality is provided.
